### 2014-06-30 Quality_Reports/PCR_bottleneck.Rmd
test

According to the **ENCODE** definitions of [quality metrics](http://encodeproject.org/ENCODE/qualityMetrics.html#definitions), one of the metrics used is the *PCR bottleneck coefficient* or *PBC*.

@@

(where N1= number of genomic locations to which EXACTLY one unique mapping read maps, and Nd = the number of genomic locations to which **AT LEAST** one unique mapping read maps, i.e. the number of non-redundant, unique mapping reads).

@@

>>>>

```{r package_options, include=FALSE}
opts_knit$set(progress = TRUE, verbose = TRUE)
```

According to the **ENCODE** definitions of [quality metrics](http://encodeproject.org/ENCODE/qualityMetrics.html#definitions), one of the metrics used is the *PCR bottleneck coefficient* or **PBC**.

@@

(where N1= number of genomic locations to which **EXACTLY** one unique mapping read maps, and Nd = the number of genomic locations to which **AT LEAST** one unique mapping read maps, i.e. the number of non-redundant, unique mapping reads).

@@

```{r init,include = TRUE,echo = TRUE}
library(parallel)
library(GenomicAlignments)
library(ggplot2)
dr ="/NO_BACKUP/KelesGroup_DongjunChung/ChIP-exo/Landick_ChIP-exo3/rawdata"
folder = c("ChIPexo","ChIPseq_PET","ChIPseq_SET")
files = lapply(folder,function(x,dr){
  ff = list.files(file.path(dr,x))
  return(ff[!grepl("bai",ff) & !grepl("sam",ff)])},dr)
names(files) = folder
message(files[[1]])
```
